A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
conclusion
conc

In this article we presented a new 
 pseudo-energetic model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs. 
We also showed that a secondary structure allows to efficiently
explore the mutational landscape and that we can benefit from the
 conserved consensus secondary structures  information
to identify and fix sequencing errors.
By combining the pseudo-energetic model and the 
mutational landscape exploration we are able  to efficiently 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

>>>>

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefit from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. We also present a
 pseudo energy model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs.

By combining those two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we are able  to efficiently 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

We must point out that our approach can only detect point wise 
sequencing errors, and only if they are located in base pairs. It 
nonetheless supplements well existing tools by using previously discarded
information.
